### 2018-02-23 paper/paper.tex
Adding paper

%% Revised 11/12/05.
%% Notice that anything written on a line that begins 
%% with  a % sign is ignored by LaTeX.
\documentclass[12pt]{amsart}

\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{noname}[theorem]{}
\newtheorem{sublemma}{}[theorem]
\newtheorem{conjecture}[theorem]{Conjecture}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\numberwithin{equation}{section}

\begin{document}

\title{Colorings of Knots}

\author{Lucas Meyers}
\address{Mathematics Department\\
Louisiana State University\\
Baton Rouge, Louisiana}
\email{lmeye22@lsu.edu}

\date{\today}

\begin{abstract}
  Empty
\end{abstract}

\maketitle

\section{Introduction}
\label{introduction}

\textbf{Citation Usage EX}~\cite[Problem 2.4.6]{jpsk}

\section*{Acknowledgements}
\begin{thebibliography}{99}

\bibitem{jpsk} Kung, J.P.S., Critical problems, in {\em Matroid  
Theory} (eds. J. E. Bonin, J.G. Oxley, and B. Servatius), {\em  
Contemporary Mathematics} {\bf 197}, Amer. Math. Soc., Providence,  
1996, pp. 1--127.

\end{thebibliography}

\end{document}

### 2018-02-28 paper/paper.tex
Section titles!
I wrote a bit, I guess

@@
 
+\newcommand{\bb}[1]{\mathbb{#1}}
+
 \begin{document}
@@
 
-\textbf{Citation Usage EX}~\cite[Problem 2.4.6]{jpsk}
+\section{Diagrams and Coloring}
+\label{sec:diagrams-coloring}
+
+\section{The Knot Group and $D_6$}
+\label{sec:knot-group-d_6}
+
+\section{$n$-colorings}
+\label{sec:n-colorings}
+
+Prior to this point we have talked about tricolourings
+of knots. However there is a natural way to extend
+our notion of colouring so that we may work with $n$
+colors as opposed to limiting ourself to 3.
+
+When it came to tricolouring knots we assigned arcs
+either blue, red, or green. However we could just as
+easily assigned numbers 0,1, or 2 to arcs and had
+our condition instead be that if we have a crossing
+as in figure
+
+\textbf{Need a crossing}
+
+That the equation $2x-y-z\equiv 0 \mod p$. We restrict
+ourselves to odd primes for technical reasons.
+Then a knot $K$ is $p$-colourable if we can assign
+a value between $0$ and $p-1$ to each arc in such a
+way that each crossing satisfies the above equation and
+at least two different colors are used.
+
+The proof that this is an invariant is precisely the same
+as it is for showing that tricolourability is an invariant.
+
+The extension of the Knot group definition of colouring is
+even faster to extend. Let $G:=\pi_1(\bb{R}^3\setminus K,*)$. Then we
+define an $n$-colouring of $K$ as a representation
+$\rho$ of $G$ into the dihedral group $D_{2n}$. As before this
+is clearly a knot invariant as there is no mention of a diagram.
+Moreover the proof that the representations of $G$ in $D_{2n}$
+correspond to colorings of diagrams follows similarly.
 

### 2018-04-01 paper/paper.tex
Draft of section 3 and part of 4

--- 2018-02-23 paper/paper.tex
@@
 
+\newcommand{\bb}[1]{\mathbb{#1}}
+
 \begin{document}
 
-\title{Colorings of Knots}
+\title{TriColorings of Knots}
 
@@
 
+\section{Diagrams and Coloring}
+\label{sec:diagrams-coloring}
+
+\section{The Knot Group}
+\label{sec:knot-group-d_6}
+
+The definition of 3-coloring is a perfectly valid definition for a knot
+invariant. However it is defined in terms of diagrams and as such
+we had to do some extra work with the Reidmeister moves to show that it
+was indeed an invariant. Ideally there would be an equivalent definition
+of coloring that does not involve diagrams. Then the fact that it is
+an invariant would be immediate and it may be possible to better tease
+out the topological property that is being captured by 3-coloring.
+
+It turns out that there is a way to define 3-coloring in this manner
+and it has to do with a construction called the Knot group. Ones first
+instinct to get a group out of a knot might be to take the fundamental
+group. However since all knots are copies of $S^1$ the fundamental group
+for any knot is $\bb{Z}$. As such we have to take advantage of its
+ambient space.
+
+\begin{definition}[Knot Group]
+  Let $K$ be a knot. Then the Knot group of $K$ is the fundamental
+  group $\pi_1(S^3\setminus K,*)$.
+\end{definition}
+
+This definition makes use of the embedding of the knot into $S^3$ and
+as such will not be identical for all knots. Naturally we need a way
+to calculate the knot group. We can do this using what is called
+the Wirtinger presentation~\cite{hatcher}.
+
+\begin{theorem}[Wirtinger]
+  Let $K$ be a knot and $D$ a diagram for $K$. Choose an
+  orientation for $D$. Then let $x_1,\ldots,x_n$
+  denote the arcs of $D$ and for each crossing give a relation
+  $r_1\ldots, r_m$ such that $r_i \equiv (x_ix_jx_i^{-1}=x_k)$ where $x_i$ is
+  the top arc of the crossing and $x_j$ is the arc underneath approaching
+  $x_k$. Then the knot group of $K$ has the presentation
+  \[
+    \pi_1(S^3\setminus K,*)\cong \langle x_1,\ldots, x_n| \rangle
+  \]
+\end{theorem}
+
+Now we give a couple of examples.
+
+\begin{example}
+  The Knot group of the unknot is
+  \[
+    \langle x_1 |\rangle \cong \bb{Z}
+  \]
+  as there are no crossings and only a single arc.
+\end{example}
+
+Followed by the trefoil knot.
+
+\begin{example}
+  The trefoil knot has three crossings and three arcs. Label it as
+  shown in figure~\ref{fig:AnnTref}. Then the Wirtinger presentation
+  of the knot group of the trefoil is
+  \[
+    \langle x_1,x_2,x_3|x_1x_2x_1^{-1}=x_3,x_3x_1x_3^{-1}=x_2,x_2x_3x_2^{-1}=x_1\rangle
+  \]
+  However the presentation of this group can be simplified to the
+  form
+  \[
+    \langle x_1,x_1| x_1x_2x_1=x_2x_1x_2\rangle
+  \]
+\end{example}
+
+\begin{figure}
+  \caption{Annotated Trefoil}
+  \label{fig:AnnTref}
+\end{figure}
+
+The knot group gives us another invariant of knots. Unfortunately
+presentations of groups can be rather difficult to work with.
+Thus in order to make the problem more tractable we instead look
+at homomorphisms from the knot group to finite groups as these
+will be determined by where we send generators. This is
+how we will redefine coloring in terms of the knot group~\cite{quickfox}.
+
+\begin{definition}[Fox 3-coloring]
+  Let $K$ be a knot and $G$ the corresponding knot group. Then a
+  Fox 3-coloring of $K$ is a homomorphism $\rho$ from
+  $G$ to the symmetries of a triangle $D_6$. We say that
+  $\rho$ is a non-trivial coloring if $\rho$ is surjective.
+
+  Thus a knot $K$ is Fox 3-colorable if there exists a nontrivial
+  Fox 3-coloring.
+\end{definition}
+
+Now a couple of examples using our prior work.
+
+\begin{example}
+  The knot group of the unknot is $\bb{Z}$. Since
+  $\bb{Z}$ has only a single generator it is not possible to
+  create a surjective homomorphism onto $D_6$ as $D_6$ has
+  two generators.
+\end{example}
+
+\begin{example}
+  As we calculated above the knot group for the trefoil is
+  \[
+    \langle x_1,x_2| x_1x_2x_1=x_2x_1x_2\rangle
+  \]
+  Similarly we can write a presentation of $D_6$ as
+  \[
+    \langle r,s| r^3=1, s^2=1,srsr=1\rangle
+  \]
+  This gives us two non-trivial Fox 3-colorings of the trefoil.
+  The first sends $x_1$ to $r$ and $x_2$ to $s$ and the
+  other swaps which generator is sent to which generator.
+\end{example}
+
+As was implied by the prior examples there is a relation between
+Fox 3-coloring and the 3-colorability of knots. In fact it turns
+out that they are exactly the same.
+
+\begin{theorem}
+  A knot $K$ has a 3-coloring if and only if there is a
+  Fox 3-coloring of $K$.
+\end{theorem}
+
+A proof of this theorem can be found within~\cite{medwid}. 
+The proof that is done relates two notions of coloring using
+the Wirtinger presentation to marry the conditions necessary
+for the existence of a 3-coloring and the existence of a Fox
+3-coloring.
+
+\section{n-coloring}
+\label{sec:n-coloring}
+
+So what are the benefits of looking at 3-coloring through
+the lens of Fox 3-coloring? As we mentioned before it is
+immediately clear that this is a knot invariant where as
+when we defined 3-coloring with diagrams. Another benefit
+is that it is more readily apparent how we can further
+extend Fox 3-coloring than extending 3-coloring. From
+the definition of 3-coloring there is some ambiguity that
+would need to be sorted out about precisely what rules need
+to change. Questions such as ``How many colors are necessary?''
+or ``What would make a crossing valid configuration?''.
+
+This is avoided with Fox 3-coloring. The only choice we made
+was that we are looking at homomorphisms to $D_6$. We could
+very easily have chosen any finite group and gotten the
+same nice structure that we had above. The reason that
+$D_6$ is the group used for Fox 3-coloring is that it is
+the group of symmetries of the triangle. We can
+define the Fox $n$-coloring similarly.
+
+\begin{definition}[Fox $n$-coloring]
+  Let $G$ be the knot group of a knot $K$. Then
+  an $n$-coloring of $K$ is a homomorphism $\rho: G\rightarrow D_{2n}$
+  where $\rho$ is called a non-trivial $n$-coloring if $\rho$ is
+  surjective.
+\end{definition}
+
+We can also extend the notion of coloring that we started
+with. However it does take more work. Instead of choosing
+the colors that we did when originally defining 3-coloring
+we could just as easily have used numbers instead. Then
+instead of requiring that each crossing either use all three
+colors or all the same it would be equivalent to each
+crossing satisfying the equation
+\[
+  2x-y-z\equiv 0 \mod 3
+\]
+where the arcs of the crossing are labeled as in figure~\ref{fig:numcolor}
+
+\begin{figure}
+
+  \caption{Colored Crossing}
+  \label{fig:numcolor}
+\end{figure}
+
+In this form it is more apparent how we could extend 3-coloring
+to arbitrary $n$
+
 \section*{Acknowledgements}
@@
 
+\bibitem{hatcher}
+
+\bibitem{quickfox}
+
+\bibitem{medwid}
+
 \end{thebibliography}

### 2018-04-22 presentation/presentation.tex
Added frames to presentation

% $Header: /Users/joseph/Documents/LaTeX/beamer/solutions/generic-talks/generic-ornate-15min-45min.en.tex,v 90e850259b8b 2007/01/28 20:48:30 tantau $

\documentclass{beamer}

% This file is a solution template for:

% - Giving a talk on some subject.
% - The talk is between 15min and 45min long.
% - Style is ornate.

% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
%
% In principle, this file can be redistributed and/or modified under
% the terms of the GNU Public License, version 2.
%
% However, this file is supposed to be a template to be modified
% for your own needs. For this reason, if you use this file as a
% template and not specifically distribute it as part of a another
% package/program, I grant the extra permission to freely copy and
% modify this file as you see fit and even to delete this copyright
% notice.

\mode<presentation>
{
  \usetheme{Warsaw}
  % or ...

  \setbeamercovered{transparent}
  % or whatever (possibly just delete it)
}

\usepackage[english]{babel}
% or whatever

\usepackage[latin1]{inputenc}
% or whatever

\usepackage{times}
\usepackage[T1]{fontenc}
% Or whatever. Note that the encoding and the font should match. If T1
% does not look nice, try deleting the line with the fontenc.

\title{Tricolorings of Knots}

\author{Lucas Meyers}
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[Louisiana State University] % (optional, but mostly needed)
{Department of Mathematics\\
Louisiana State University}

\date[Short Occasion] % (optional)
{\today}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\section{Tricoloring Knots}

\begin{frame}{Make Titles Informative. Use Uppercase Letters.}{Subtitles are optional.}
  % - A title should summarize the slide in an understandable fashion
  %   for anyone how does not follow everything on the slide itself.

  \begin{itemize}
  \item
    Use \texttt{itemize} a lot.
  \item
    Use very short sentences or short phrases.
  \end{itemize}
\end{frame}

\begin{frame}{Make Titles Informative.}

  You can create overlays\dots
  \begin{itemize}
  \item using the \texttt{pause} command:
    \begin{itemize}
    \item
      First item.
      \pause
    \item    
      Second item.
    \end{itemize}
  \item
    using overlay specifications:
    \begin{itemize}
    \item<3->
      First item.
    \item<4->
      Second item.
    \end{itemize}
  \item
    using the general \texttt{uncover} command:
    \begin{itemize}
      \uncover<5->{\item
        First item.}
      \uncover<6->{\item
        Second item.}
    \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Knot Definition}

\end{frame}

\begin{frame}
  \frametitle{Unknot}

\end{frame}

\begin{frame}
  \frametitle{Trefoil}

\end{frame}

\begin{frame}
  \frametitle{Figure-Eight}

\end{frame}

\begin{frame}
  \frametitle{Equivalence}

\end{frame}

\begin{frame}
  \frametitle{Diagrams}

\end{frame}

\begin{frame}
  \frametitle{Reidmeister Moves}

\end{frame}

\begin{frame}
  \frametitle{Type I}

\end{frame}

\begin{frame}
  \frametitle{Type II}

\end{frame}

\begin{frame}
  \frametitle{Type III}

\end{frame}

\begin{frame}
  \frametitle{Tricoloring}

\end{frame}

\begin{frame}
  \frametitle{Type I}

\end{frame}

\begin{frame}
  \frametitle{Type II}

\end{frame}

\begin{frame}
  \frametitle{Type II}

\end{frame}

\begin{frame}
  \frametitle{Type III}

\end{frame}

\begin{frame}
  \frametitle{Type III}

\end{frame}

\begin{frame}
  \frametitle{Uncolorability of the Unknot}

\end{frame}

\begin{frame}
  \frametitle{Colorability of the Trefoil}

\end{frame}

\begin{frame}
  \frametitle{Uncolorability of the Figure-Eight Knot}

\end{frame}

\section{The Knot Group}

\begin{frame}
  \frametitle{Knot Group}

\end{frame}

\begin{frame}
  \frametitle{Knot Group of the Unknot}

\end{frame}

\begin{frame}
  \frametitle{Wirtinger Presentation}

\end{frame}

\begin{frame}
  \frametitle{Knot Group of the Trefoil}

\end{frame}

\begin{frame}
  \frametitle{Fox 3-Colorings}

\end{frame}

\begin{frame}
  \frametitle{Fox 3-Colorings of the Unknot and Trefoil}

\end{frame}

\begin{frame}
  \frametitle{Equivalence of Tricoloring and Fox 3-Coloring}

\end{frame}

\section{Consequences}

\begin{frame}
  \frametitle{Consequences}

\end{frame}

\begin{frame}
  \frametitle{Extending Tricolorability}

\end{frame}

\begin{frame}
  \frametitle{5-Coloring of the Figure-Eight Knot}

\end{frame}

\end{document}

### 2018-04-22 presentation/presentation.tex
Added presentation content, missing pauses

@@
 
+\graphicspath{{images/}}
+
 \title{Tricolorings of Knots}
@@
 
-\begin{frame}{Make Titles Informative. Use Uppercase Letters.}{Subtitles are optional.}
-  % - A title should summarize the slide in an understandable fashion
-  %   for anyone how does not follow everything on the slide itself.
-
+\begin{frame}
+  \frametitle{Knot Definition}
   \begin{itemize}
-  \item
-    Use \texttt{itemize} a lot.
-  \item
-    Use very short sentences or short phrases.
+  \item A \textit{Knot} is a simple closed curve in $S^3$ ($\mathbb{R}^3\cup \{\infty\}$)
   \end{itemize}
@@
 
-\begin{frame}{Make Titles Informative.}
+\begin{frame}
+  \frametitle{Unknot}
+  \begin{center}
+    \includegraphics[scale=.4]{unknot}  
+  \end{center}
+\end{frame}
 
-  You can create overlays\dots
+\begin{frame}
+  \frametitle{Trefoil}
+  \begin{center}
+    \includegraphics[scale=.4]{trefoil}    
+  \end{center}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Figure-Eight}
+  \begin{center}
+    \includegraphics[scale=.4]{figure-eight}
+  \end{center}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Equivalence}
   \begin{itemize}
-  \item using the \texttt{pause} command:
+  \item All knots are homeomorphic to $S^1$.
+  \item Two knots $K$ and $J$ are \textit{Ambient Isotopic}
+    if there is a homotopy $H:S^3\times[0,1]\rightarrow S^3$ such that
     \begin{itemize}
-    \item
-      First item.
-      \pause
-    \item    
-      Second item.
-    \end{itemize}
-  \item
-    using overlay specifications:
-    \begin{itemize}
-    \item<3->
-      First item.
-    \item<4->
-      Second item.
-    \end{itemize}
-  \item
-    using the general \texttt{uncover} command:
-    \begin{itemize}
-      \uncover<5->{\item
-        First item.}
-      \uncover<6->{\item
-        Second item.}
+    \item $H(x,0)$ is the identity on $S^3$
+    \item The image $H(K,1)$ is $J$
+    \item For each fixed $t\in[0,1]$ the map $H(x,t)$ is a
+      homeomorphism.
     \end{itemize}
@@
 \begin{frame}
-  \frametitle{Knot Definition}
+  \frametitle{Diagrams}
+  \begin{itemize}
+  \item A \textit{diagram} $D$ of a knot $K$ is a projection of
+    $K$ to a plane such that
+    \begin{itemize}
+    \item We preserve over and under crossing information
+    \item Only two points or fewer may be projected to the same
+      point
+    \item All crossings must be either overcrossings or undercrossings.
 
-\end{frame}
-
-\begin{frame}
-  \frametitle{Unknot}
-
-\end{frame}
-
-\begin{frame}
-  \frametitle{Trefoil}
-
-\end{frame}
-
-\begin{frame}
-  \frametitle{Figure-Eight}
-
-\end{frame}
-
-\begin{frame}
-  \frametitle{Equivalence}
-
-\end{frame}
-
-\begin{frame}
-  \frametitle{Diagrams}
-
+    \end{itemize}
+    \begin{center}
+      \includegraphics[scale=.2]{bad-crossing}  
+    \end{center}
+  \end{itemize}
 \end{frame}
@@
   \frametitle{Reidmeister Moves}
+  \begin{itemize}
+  \item Diagrams for a knot are not unique.
+  \end{itemize}
+  \begin{columns}
+    \begin{column}{.5\textwidth}
+      \begin{center}
+        \includegraphics[scale=.3]{unknot}
+      \end{center}
+    \end{column}
+    \begin{column}{.5\textwidth}
+      \begin{center}
+        \includegraphics[scale=.3]{ugly-unknot}
+      \end{center}
+    \end{column}
+  \end{columns}
+\end{frame}
 
+\begin{frame}
+  \frametitle{Reidmeister Moves}
+  \begin{itemize}
+  \item \textbf{Theorem:} Two knots $K$ and $J$ are ambient isotopic if, and
+    only if, their diagrams are related by a finite sequence of Reidmeister moves
+    and planar isotopy.
+  \end{itemize}
 \end{frame}
@@
   \frametitle{Type I}
-
+  \begin{center}
+    \includegraphics[scale=.4]{t1}
+  \end{center}
 \end{frame}
@@
   \frametitle{Type II}
-
+  \begin{center}
+    \includegraphics[scale=.4]{t2}
+  \end{center}
 \end{frame}
@@
   \frametitle{Type III}
-
+  \begin{center}
+    \includegraphics[scale=.6]{t3}
+  \end{center}
 \end{frame}
@@
   \frametitle{Tricoloring}
-
+  \begin{itemize}
+  \item A \textit{tricoloring} of a diagram is an assignment
+    of one of three colors to each arc such that for all crossings
+    \begin{itemize}
+    \item Only a single color is present
+    \item All three colors are present
+    \end{itemize}
+  \item A tricoloring is \textit{nontrivial} if at least two colors are used
+  \item \textbf{Theorem:} The existence of a non-trivial tricoloring is a knot
+    invariant. Such a knot is called tricolorable (or $3$-colorable).
+  \end{itemize}
 \end{frame}
@@
   \frametitle{Type I}
-
+  \begin{center}
+    \includegraphics[scale=.4]{t1-c}
+  \end{center}
 \end{frame}
@@
   \frametitle{Type II}
-
+  \begin{center}
+    \includegraphics[scale=.4]{t2-c1}
+  \end{center}
 \end{frame}
@@
   \frametitle{Type II}
-
+  \begin{center}
+    \includegraphics[scale=.4]{t2-c2}
+  \end{center}
 \end{frame}
@@
   \frametitle{Type III}
-
+  \begin{center}
+    \includegraphics[scale=.6]{t3-c1}
+  \end{center}
 \end{frame}
@@
   \frametitle{Type III}
+  \begin{center}
+    \includegraphics[scale=.6]{t3-c2}
+  \end{center}
+\end{frame}
 
+\begin{frame}
+  \frametitle{Type III}
+  \begin{center}
+    \includegraphics[scale=.6]{t3-c3}
+  \end{center}
 \end{frame}
@@
   \frametitle{Uncolorability of the Unknot}
-
+  \begin{center}
+    \includegraphics[scale=.4]{unknot}
+  \end{center}
 \end{frame}
@@
   \frametitle{Colorability of the Trefoil}
-
+  \begin{center}
+    \includegraphics[scale=.4]{trefoil-c}
+  \end{center}
 \end{frame}
@@
   \frametitle{Uncolorability of the Figure-Eight Knot}
-
+  \begin{center}
+    \includegraphics[scale=.4]{figure-eight}
+  \end{center}
 \end{frame}
@@
   \frametitle{Knot Group}
-
+  \begin{itemize}
+  \item Since all knots are homeomorphic to $S^1$ their
+    fundamental groups are isomorphic to $\mathbb{Z}$.
+  \item Given a knot $K$, the \textit{knot group} is
+    the fundamental group of the knots complement  $\pi_1(S^3\setminus K,*)$
+  \end{itemize}
 \end{frame}
@@
   \frametitle{Knot Group of the Unknot}
-
+  \begin{center}
+    \includegraphics[scale=.3]{unknot}
+  \end{center}
+  \begin{itemize}
+  \item The knot group of the unknot is
+    $\pi_1(S^3\setminus K,*)=\mathbb{Z}$ generated by the loop through the
+    unknot's.
+  \end{itemize}
 \end{frame}
@@
   \frametitle{Wirtinger Presentation}
-
+  \begin{itemize}
+  \item For other knots we use a tool called the \textit{Wirtinger Presentation}.
+  \item Let $K$ be a knot and $D$ a diagram for $K$. Choose an orientation of $D$.
+    Let $x_1,\ldots, x_n$ denote the arcs of $D$ and, for each crossing, give a
+    relation $r_1,\ldots, r_m$ such that $r_i\equiv (x_i x_j x_i^{-1})$ where, when approaching
+    $x_k$ is the arc leaving the crossing, the top arc is $x_i$ and the bottom arc entering
+    is $x_j$.
+  \item Then the knot group of $K$ has presentation
+    \[
+      \pi_1(S^3\setminus K) \equiv \langle x_1,\ldots, x_n| r_1,\ldots r_m\rangle
+    \]
+  \end{itemize}
 \end{frame}
@@
   \frametitle{Knot Group of the Trefoil}
-
+  \begin{center}
+    \includegraphics[scale=.25]{annotated-trefoil}
+  \end{center}
+  \begin{itemize}
+  \item From this diagram the knot group of the trefoil is 
+    \[
+      \langle x_1,x_2,x_3|x_1x_2x_1^{-1}=x_3,x_3x_1x_3^{-1}=x_2,x_2x_3x_2^{-1}=x_1\rangle
+    \]
+  \item Which simplifies to $\langle x_1,x_2|x_1 x_2 x_1= x_2 x_1 x_2\rangle$
+  \end{itemize}
 \end{frame}
@@
   \frametitle{Fox 3-Colorings}
-
+  \begin{itemize}
+  \item A \textit{Fox $3$-coloring} is a homomorphism $\rho$ from
+    the knot group the symmetry group $D_6$ of an equilateral
+    triangle.
+  \item A Fox $3$-coloring is nontrivial if $\rho$ is surjective.
+  \end{itemize}
 \end{frame}
@@
   \frametitle{Fox 3-Colorings of the Unknot and Trefoil}
-
+  \begin{itemize}
+  \item There is no nontrivial Fox $3$-coloring of the unknot as
+    $D_6$ has two generators and the knot group of the unknot, $\mathbb{Z}$,
+    only has one.
+  \item We can give a nontrivial Fox $3$-coloring of the trefoil,
+    $\langle x_1,x_2|x_1 x_2 x_1= x_2 x_1 x_2\rangle$, using the presentation of $D_6$ as
+    \[
+      \langle r,s| r^3=s^2=1, srsr=1\rangle
+    \]
+    by mapping $x_1$ to $r$ and $x_2$ to $s$ or vice versa.
+  \item This gives us two nontrivial Fox $3$-colorings of the trefoil.
+   \end{itemize}
 \end{frame}
@@
   \frametitle{Equivalence of Tricoloring and Fox 3-Coloring}
-
+  \begin{itemize}
+  \item \textbf{Theorem:} A Knot $K$ has a $3$-coloring if, and only if,
+    there is a Fox $3$-coloring of $K$.
+  \end{itemize}
 \end{frame}
@@
   \frametitle{Consequences}
-
+  \begin{itemize}
+  \item Since for any two groups $G$ and $H$ the homomorphisms
+    $\hom(G,H)$ form a group this implies that colorings of knots
+    also form a group.
+  \item Unlike with tricolorability it more obvious how to extend
+    Fox $3$-colorings to an arbitrary number of colors.
+    \begin{itemize}
+    \item A \textit{Fox $n$-coloring} of a knot $K$ is a homomorphism from
+      the knot group of $K$ to $D_{2n}$.
+    \end{itemize}
+  \item Given any group $G$ we can define a \textit{Fox $G$-coloring}
+    as a homomorphism from the knot group of $K$ to the group $G$.
+    \begin{itemize}
+    \item If $G$ is a finite group then searching for nontrivial $G$-colorings
+      is very fast to compute.
+    \item This can be done by sending generators to generators and checking
+      that the relations hold.
+    \end{itemize}
+  \end{itemize}
 \end{frame}
@@
   \frametitle{Extending Tricolorability}
-
+  \begin{itemize}
+  \item We can also use the fact that Fox $3$-colorings and tricolorability
+    are equivalent to guide us in extending the notion of $n$-colorings
+    to diagrams as well.
+  \item Instead of assigning colors to each arc we use elements of $\mathbb{Z}_n$.
+  \item Then a diagram has a nontrivial coloring if at least two numbers are used
+    and for each crossing, if we label the overcrossing arc $x$ and the two
+    undercrossing arcs as $y$ and $z$, the following equation is satisfied
+    \[
+      2x-y-z \equiv 0 \mod n
+    \]
+  \end{itemize}
 \end{frame}
@@
   \frametitle{5-Coloring of the Figure-Eight Knot}
-
+  \begin{itemize}
+  \item Recall that the figure-eight knot was not $3$-colorable.
+    However it is $5$-colorable.
+  \end{itemize}
+  \begin{center}
+    \includegraphics[scale=.4]{figure-eight-c}
+  \end{center}
 \end{frame}

### 2018-04-24 presentation/presentation.tex
Added pauses to talk
Finished presentation

@@
   \item All knots are homeomorphic to $S^1$.
+    \pause
   \item Two knots $K$ and $J$ are \textit{Ambient Isotopic}
@@
     \begin{itemize}
+      \pause
     \item $H(x,0)$ is the identity on $S^3$
+      \pause
     \item The image $H(K,1)$ is $J$
+      \pause
     \item For each fixed $t\in[0,1]$ the map $H(x,t)$ is a
@@
     \begin{itemize}
+      \pause
+    \item At most two points can be projected to the same point on the plane.
+      \pause
+    \item All crossings must be either overcrossings or undercrossings.
+      \pause
     \item We preserve over and under crossing information      
-    \item Only two points or fewer may be projected to the same
-      point
-    \item All crossings must be either overcrossings or undercrossings.
-
     \end{itemize}
     \begin{center}
-      \includegraphics[scale=.2]{bad-crossing}  
+      \visible<3->{\includegraphics[scale=.2]{bad-crossing}}
     \end{center}
@@
       \begin{center}
-        \includegraphics[scale=.3]{unknot}
+        \visible<2->{\includegraphics[scale=.3]{unknot}}
       \end{center}
@@
       \begin{center}
-        \includegraphics[scale=.3]{ugly-unknot}
+        \visible<2->{\includegraphics[scale=.3]{ugly-unknot}}
       \end{center}
@@
     \begin{itemize}
+      \pause
     \item Only a single color is present
+      \pause
     \item All three colors are present
     \end{itemize}
+    \pause
   \item A tricoloring is \textit{nontrivial} if at least two colors are used
+    \pause
   \item \textbf{Theorem:} The existence of a non-trivial tricoloring is a knot
@@
 
+% Add a frame by frame attempt of this
+
 \begin{frame}
@@
     \includegraphics[scale=.4]{figure-eight}
+  \end{center}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Uncolorability of the Figure-Eight Knot}
+  \begin{center}
+    \includegraphics[scale=.4]{figure-eight-bad1}
+  \end{center}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Uncolorability of the Figure-Eight Knot}
+  \begin{center}
+    \includegraphics[scale=.4]{figure-eight-bad2}
+  \end{center}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Uncolorability of the Figure-Eight Knot}
+  \begin{center}
+    \includegraphics[scale=.4]{figure-eight-bad3}
+  \end{center}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Uncolorability of the Figure-Eight Knot}
+  \begin{center}
+    \includegraphics[scale=.4]{figure-eight-bad4}
   \end{center}
@@
     fundamental groups are isomorphic to $\mathbb{Z}$.
+    \pause
   \item Given a knot $K$, the \textit{knot group} is
@@
   \begin{itemize}
+    \pause
   \item The knot group of the unknot is
@@
   \item For other knots we use a tool called the \textit{Wirtinger Presentation}.
+    \pause
   \item Let $K$ be a knot and $D$ a diagram for $K$. Choose an orientation of $D$.
     Let $x_1,\ldots, x_n$ denote the arcs of $D$ and, for each crossing, give a
-    relation $r_1,\ldots, r_m$ such that $r_i\equiv (x_i x_j x_i^{-1})$ where, when approaching
+    relation $r_1,\ldots, r_m$ such that $r_i\equiv (x_i x_j x_i^{-1}=x_k)$ where, when approaching
     $x_k$ is the arc leaving the crossing, the top arc is $x_i$ and the bottom arc entering
     is $x_j$.
+    \pause
   \item Then the knot group of $K$ has presentation
@@
       \langle x_1,x_2,x_3|x_1x_2x_1^{-1}=x_3,x_3x_1x_3^{-1}=x_2,x_2x_3x_2^{-1}=x_1\rangle
-    \]
+    \]\pause
   \item Which simplifies to $\langle x_1,x_2|x_1 x_2 x_1= x_2 x_1 x_2\rangle$
@@
     triangle.
+    \pause
   \item A Fox $3$-coloring is nontrivial if $\rho$ is surjective.
@@
     only has one.
+    \pause
   \item We can give a nontrivial Fox $3$-coloring of the trefoil,
@@
     by mapping $x_1$ to $r$ and $x_2$ to $s$ or vice versa.
+    \pause
   \item This gives us two nontrivial Fox $3$-colorings of the trefoil.
@@
     also form a group.
+    \pause
   \item Unlike with tricolorability it more obvious how to extend
@@
     \begin{itemize}
+      \pause
     \item A \textit{Fox $n$-coloring} of a knot $K$ is a homomorphism from
@@
     \end{itemize}
+    \pause
   \item Given any group $G$ we can define a \textit{Fox $G$-coloring}
@@
     \begin{itemize}
+      \pause
     \item If $G$ is a finite group then searching for nontrivial $G$-colorings
       is very fast to compute.
+      \pause
     \item This can be done by sending generators to generators and checking
@@
     to diagrams as well.
+    \pause
   \item Instead of assigning colors to each arc we use elements of $\mathbb{Z}_n$.
+    \pause
   \item Then a diagram has a nontrivial coloring if at least two numbers are used
@@
   \begin{center}
-    \includegraphics[scale=.4]{figure-eight-c}
+    \visible<2->{\includegraphics[scale=.4]{figure-eight-c}}
   \end{center}

### 2018-04-24 presentation/presentation.tex
Added periods

@@
   \begin{itemize}
-  \item A \textit{Knot} is a simple closed curve in $S^3$ ($\mathbb{R}^3\cup \{\infty\}$)
+  \item A \textit{Knot} is a simple closed curve in $S^3$ ($\mathbb{R}^3\cup \{\infty\}$).
   \end{itemize}
@@
   \item Two knots $K$ and $J$ are \textit{Ambient Isotopic}
-    if there is a homotopy $H:S^3\times[0,1]\rightarrow S^3$ such that
+    if there is a homotopy $H:S^3\times[0,1]\rightarrow S^3$ such that:
     \begin{itemize}
       \pause
-    \item $H(x,0)$ is the identity on $S^3$
+    \item $H(x,0)$ is the identity on $S^3$.
       \pause
-    \item The image $H(K,1)$ is $J$
+    \item The image $H(K,1)$ is $J$.
       \pause
@@
   \item A \textit{diagram} $D$ of a knot $K$ is a projection of
-    $K$ to a plane such that
+    $K$ to a plane such that:
     \begin{itemize}
@@
       \pause
-    \item We preserve over and under crossing information      
+    \item We preserve over and under crossing information.
     \end{itemize}
@@
   \item A \textit{tricoloring} of a diagram is an assignment
-    of one of three colors to each arc such that for all crossings
+    of one of three colors to each arc such that for all crossings:
     \begin{itemize}
       \pause
-    \item Only a single color is present
+    \item Only a single color is present.
       \pause
-    \item All three colors are present
+    \item All three colors are present.
     \end{itemize}
     \pause
-  \item A tricoloring is \textit{nontrivial} if at least two colors are used
+  \item A tricoloring is \textit{nontrivial} if at least two colors are used.
     \pause
@@
   \item Given a knot $K$, the \textit{knot group} is
-    the fundamental group of the knots complement  $\pi_1(S^3\setminus K,*)$
+    the fundamental group of the knots complement  $\pi_1(S^3\setminus K,*)$.
   \end{itemize}
@@
     \[
-      \pi_1(S^3\setminus K) \equiv \langle x_1,\ldots, x_n| r_1,\ldots r_m\rangle
+      \pi_1(S^3\setminus K) \equiv \langle x_1,\ldots, x_n| r_1,\ldots r_m\rangle.
     \]
@@
     \[
-      \langle x_1,x_2,x_3|x_1x_2x_1^{-1}=x_3,x_3x_1x_3^{-1}=x_2,x_2x_3x_2^{-1}=x_1\rangle
+      \langle x_1,x_2,x_3|x_1x_2x_1^{-1}=x_3,x_3x_1x_3^{-1}=x_2,x_2x_3x_2^{-1}=x_1\rangle.
     \]\pause
-  \item Which simplifies to $\langle x_1,x_2|x_1 x_2 x_1= x_2 x_1 x_2\rangle$
+  \item Which simplifies to $\langle x_1,x_2|x_1 x_2 x_1= x_2 x_1 x_2\rangle$.
   \end{itemize}

### 2018-04-25 paper/paper.tex
Oxley revisions completed

--- 2018-02-23 paper/paper.tex
@@
-%% Revised 11/12/05.
-%% Notice that anything written on a line that begins 
-%% with  a % sign is ignored by LaTeX.
 \documentclass[12pt]{amsart}
@@
 \usepackage{amssymb}
+\usepackage{graphicx}
+
+\graphicspath{{images/}}
 
@@
 
+\newcommand{\bb}[1]{\mathbb{#1}}
+\newcommand{\ds}{.3}
+
 \begin{document}
 
-\title{Colorings of Knots}
+\title{TriColorings of Knots}
 
@@
 \begin{abstract}
-  Empty
+  Tricoloring is a knot invariant that differentiates knots
+  based on whether or knot their diagram can be colored in a
+  certain way with three colors. In this paper, we introduce knots
+  and define tricolorability in terms of both knot diagrams
+  and the knot group. We then mention extensions of the notions
+  of tricolorability to arbitrary $n$-coloring.
 \end{abstract}
@@
 \maketitle
+\textbf{TODO}:
+\begin{enumerate}
+\item Remove \textbf{TODO}
+\item Iron out Figure/image placement before final edition. Too early
+  now. Wait till revision is done.
+\item Passive voice/adverbs (Hemingway App)
+\end{enumerate}
 
@@
 
-\textbf{Citation Usage EX}~\cite[Problem 2.4.6]{jpsk}
+One common pattern we see in mathematics is a concern with how
+certain objects fit inside other objects. Knot theory studies this
+sort of problem. Given a circle $S^1$ what different ways can we embed
+it into $\bb{R}^3$ or $\bb{R}^3$  with an additional point at infinity ($S^3$)?
+A typical drawing of a knot can be seen in Figure~\ref{fig:figure-eight}.
 
-\section*{Acknowledgements}
+\begin{figure}
+  \includegraphics[scale=\ds]{figure-eight}
+  \caption{Figure-eight knot}
+  \label{fig:figure-eight}
+\end{figure}
+
+Naturally, once we begin to consider knots, we are also led to consider
+how we might tell them apart or rather when they should be the same
+at all. Intuitively, the knot in Figure~\ref{fig:figure-eight} should
+be considered the same as that in Figure~\ref{fig:figure-eight-t} but should be
+different from that of trefoil seen in Figure~\ref{fig:trefoil}. In
+the next section, we will see the definition of a knot, how to define their
+equivalence in a sensible way, followed by a method to differentiate them
+called tricolorability. Afterwards, we will look at an alternative definition
+of tricolorability. Then we will introduce notions of how one may consider
+coloring knots with more than three colors.
+
+\begin{figure}
+  \includegraphics[scale=\ds]{figure-eight-t}
+  \caption{Figure-eight with a twist}
+  \label{fig:figure-eight-t}
+\end{figure}
+
+\section{Diagrams and Coloring}
+\label{sec:diagrams-coloring}
+
+In this paper we will follow the conventions of Charles
+Livingston~\cite{Livingston}. To begin, we give the definition of a knot.
+
+\begin{definition}
+  A \textit{knot} is a simple closed curve in $\bb{R}^3$(or $S^3$).
+\end{definition}
+
+Now there are two issues that we need to consider before moving forward.
+The first is our notion of equivalence. Unfortunately, a homeomorphism from
+one knot to another is too weak a notion of equivalence. Instead we will
+use the following:
+
+\begin{definition}
+  Two knots $K,J$ are \textit{ambient isotopic} if there is a homotopy on the ambient
+  space $H:S^3\times [0,1]\rightarrow S^3$ if $H(x,0)$ is the identity and the
+  image $H(K,1)=J$.
+\end{definition}
+
+The second issue of initial concern is that we will be considering a subset of knots called tame. A knot
+is \textit{tame} if it is ambient isotopic to a piecewise linear knot. A
+knot that is not tame is called \textit{wild} and a drawing of an example of such a knot
+seen in Figure~\ref{fig:wild}. The knot in question has a decreasing sequence of
+components that cannot be made linear. Wild knots have some more pathological
+properties and to keep things simple and consistent we will restrict ourselves to
+tame knots.
+
+\begin{figure}
+  \includegraphics[scale=\ds]{wild}
+  \caption{Wild knot}
+  \label{fig:wild}
+\end{figure}
+
+When we give the initial definition of  tricolorability we will not work
+directly with the curves themselves. Instead we will deal with diagrams
+of the knots. All drawings of knots in this paper are examples of diagrams.
+
+\begin{definition}
+  A \textit{diagram} $D$ for a knot $K$ is a projection of $K$ to a plane
+  such that:
+  \begin{itemize}
+  \item At most two points are sent to the same location on the plane.
+    These are called \textit{crossings}.
+  \item For any two crossings there are open disjoint neighborhoods of each.
+  \item All crossings must be either overcrossings or undercrossings.
+  \end{itemize}
+  Note that all figures in this paper are diagrams of knots.
+\end{definition}
+
+When we project to a plane there is a loss of information that occurs. This
+is why we must denote all crossings as either overcrossings or undercrossings.
+This allows one to recover the knot in its entirity from the diagram. Otherwise
+it would be ambiguous what knot is recovered. The segments that make up the diagram
+are called \textit{arcs}.
+
+There is one other unfortunate occurrence
+from moving to diagrams. It is that there are infinitely many diagrams
+for a given knot. Moreover actually telling whether two diagrams denote
+the same knot is extremely difficult although it is decidable and moreover
+belongs to NP~\cite{Poonen}.
+
+It turns out that there are three ``moves'' along with planar isotopy
+that we can apply to diagrams that will allow us to completely characterize
+when two diagrams correspond to the same knot.
+
+\begin{definition}
+  The \textit{Reidmeister moves} are the moves labeled in Figure~\ref{fig:reidmeister}.
+  They are referred to as type-I, type-II, or type-III moves respectively.
+
+  \begin{figure}
+    \includegraphics[scale=\ds]{reidmeister}
+    \caption{Reidmeister moves of type I, II, and III}
+    \label{fig:reidmeister}
+  \end{figure}
+\end{definition}
+
+We will use, without proof, the following theorem about Reidmeister moves.
+
+\begin{theorem}
+  Two knots $K$ and $J$ are ambient isotopic if and only if their diagrams
+  are related by a finite sequence of Reidmeister moves and planar isotopy.
+\end{theorem}
+
+The importance of Reidmeister moves and diagrams becomes apparent
+in defining invariants of knots. If we define an invariant on diagrams and show
+that it does not change under planar isotopy or the Reidmeister moves, then
+it will also act as an invariant on knots. This is precisely the method we
+will use with our initial definition of tricolorability.
+
+There are two knots that we will return to over and over again in this paper
+as they are the simplest examples of knots for which tricolorability
+differentiates them. The simplest knot is the \textit{unknot} (see Figure~\ref{fig:unknot}), which
+is unique in that it has a diagram with no crossings whatsoever. The
+other is the \textit{trefoil} shown in Figure~\ref{fig:trefoil}.
+
+\begin{figure}
+  \includegraphics[scale=\ds]{unknot}
+  \caption{Unknot}
+  \label{fig:unknot}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[scale=\ds]{trefoil}
+  \caption{Trefoil knot}
+  \label{fig:trefoil}
+\end{figure}
+
+With that in mind let us introduce tricolorability.
+
+\begin{definition}
+  Let $K$ be a knot with diagram $D$. Then a \textit{tricoloring ($3$-coloring)}
+  of $K$ is an assignment to each arc one of three colors
+  such that at each crossing either all colors appear or
+  only single color appears. A tricoloring is called \textit{non-trivial}
+  if at least two colors are used.
+\end{definition}
+
+We will use the colors red, green, and blue as our colors.
+Now we must show that tricoloring is in fact an invariant.
+
+\begin{theorem}
+  The existence of a non-trivial $3$-coloring for some diagram is a
+  knot invariant.
+\end{theorem}
+
+\begin{proof}
+  Let $K$ be a knot with diagram $D$. We must show that, given a coloring
+  for $D$, we can color any diagram of $K$. First note that planar isotopy
+  does not affect the crossings for $D$ and, as such, does not change the
+  $3$-colorability.
+
+  Next we will have a series of pictures that demonstrate the possibilities
+  for type-I, type-II, and type-III moves respectively.
+
+  For type-I we have there only a single case as a type-I move acts only on
+  a single arc.
+  \begin{figure}
+    \includegraphics[scale=\ds]{t1-c}
+    \caption{type-I}
+    \label{fig:t1-c}
+  \end{figure}
+
+  For type-II, there are two cases either both strands have the same color
+  or they are different.
+  \begin{figure}
+    \includegraphics[scale=\ds]{t2-c}
+    \caption{type-II}
+    \label{fig:t2-c}
+  \end{figure}
+
+  Finally, for type-III moves there are several cases based on
+  the colors of the strands entering. We will demonstrate
+  three such cases and the rest are similar.
+  \begin{figure}
+    \includegraphics[scale=\ds]{t3-c}
+    \caption{type-III}
+    \label{fig:t3-c}
+  \end{figure}
+
+  Thus if a diagram $D$ for a knot $K$ has a $3$-coloring, then
+  any diagram for $K$ has a $3$-coloring. Therefore $3$-colorability
+  is a knot invariant.
+\end{proof}
+
+An immediate consequence of this is that the unknot and the trefoil
+knot are in fact not identical. We can see this because the unknot
+is not tricolorable as it only has a single arc. However, the
+trefoil can be colored as in Figure~\ref{fig:trefoil-c}.
+
+\begin{figure}
+  \includegraphics[scale=\ds]{trefoil-c}
+  \caption{Colored trefoil}
+  \label{fig:trefoil-c}
+\end{figure}
+
+\section{The Knot Group}
+\label{sec:knot-group-d_6}
+
+The definition of $3$-coloring is a perfectly valid definition for a knot
+invariant. However, it is defined in terms of diagrams and, as such,
+we had to do some extra work with the Reidmeister moves to show that it
+was indeed an invariant. Ideally, there would be an equivalent definition
+of coloring that does not involve diagram, but rather, only involves
+the knot and its embedding into $S^3$. Then it may be easier to tease
+out what topological properties are being captured by $3$-coloring.
+
+It turns out that there is a way to define $3$-coloring in this manner
+and it has to do with a construction called the knot group. Ones first
+instinct to get a group out of a knot might be to take the fundamental
+group. However, since all knots are copies of $S^1$, the fundamental group
+for any knot is $\bb{Z}$. As such, we have to take advantage of its
+ambient space.
+
+\begin{definition}
+  Let $K$ be a knot. Then the \textit{knot group} of $K$ is the fundamental
+  group $\pi_1(S^3\setminus K,*)$.
+\end{definition}
+
+This definition makes use of the embedding of the knot into $S^3$ and
+so will not be identical for all knots. Naturally, we need a way
+to calculate the knot group. We can do this using what is called
+the \textit{Wirtinger presentation}~\cite{hatcher}.
+
+\begin{theorem}[Wirtinger]
+  Let $K$ be a knot and $D$ a diagram for $K$. Choose an
+  orientation for $D$. Let $x_1,\ldots,x_n$
+  denote the arcs of $D$ and, for each crossing, give a relation
+  $r_1\ldots, r_m$ such that $r_i \equiv (x_ix_jx_i^{-1}=x_k)$ where, when approaching
+  $x_k$ is the arc leaving the crossing, the top arc is $x_i$ and the bottom
+  arc entering is $x_j$. Then the knot group of $K$ has the presentation
+  \[
+    \pi_1(S^3\setminus K,*)\cong \langle x_1,\ldots, x_n| r_1,\ldots,r_m\rangle
+  \]
+\end{theorem}
+
+Now we give a couple of examples.
+
+\begin{example}
+  The knot group of the unknot is
+  \[
+    \langle x_1 |\rangle \cong \bb{Z}
+  \]
+  as there are no crossings and only a single arc.
+\end{example}
+
+\begin{example}
+  The trefoil knot has three crossings and three arcs. Label it as
+  shown in Figure~\ref{fig:annotated-trefoil}. Then the Wirtinger presentation
+  of the knot group of the trefoil is
+  \[
+    \langle x_1,x_2,x_3|x_1x_2x_1^{-1}=x_3,x_3x_1x_3^{-1}=x_2,x_2x_3x_2^{-1}=x_1\rangle
+  \]
+  However, the presentation of this group can be simplified to the
+  form
+  \[
+    \langle x_1,x_2| x_1x_2x_1=x_2x_1x_2\rangle
+  \]
+\end{example}
+
+\begin{figure}
+  \includegraphics[scale=\ds]{annotated-trefoil}
+  \caption{Annotated Trefoil}
+  \label{fig:annotated-trefoil}
+\end{figure}
+
+The knot group gives us another invariant of knots. Unfortunately,
+presentations of groups can be rather difficult to work with.
+Thus, to make the problem more tractable, we instead look
+at homomorphisms from the knot group to finite groups as these
+will be determined by where we send generators. This is
+how we will redefine coloring in terms of the knot group~\cite{quickfox}.
+
+\begin{definition}
+  Let $K$ be a knot and $G$ the corresponding knot group. Then a
+  \textit{Fox $3$-coloring} of $K$ is a homomorphism $\rho$ from
+  $G$ to the symmetry group $D_6$ of an equilateral triangle. We say that
+  $\rho$ is a \textit{non-trivial coloring} if $\rho$ is surjective.
+
+  Thus a knot $K$ is \textit{Fox $3$-colorable} if there exists a nontrivial
+  Fox $3$-coloring.
+\end{definition}
+
+Now a couple of examples using our prior work.
+
+\begin{example}
+  Recall that the knot group of the unknot is $\bb{Z}$. Since
+  $\bb{Z}$ has only a single generator, it is not possible to
+  create a surjective homomorphism onto $D_6$ as $D_6$ has
+  two generators.
+\end{example}
+
+\begin{example}
+  As we calculated above, the knot group for the trefoil is
+  \[
+    \langle x_1,x_2| x_1x_2x_1=x_2x_1x_2\rangle.
+  \]
+  Similarly, we can write a presentation of $D_6$ as
+  \[
+    \langle r,s| r^3=1, s^2=1,srsr=1\rangle.
+  \]
+  This gives us two non-trivial Fox $3$-colorings of the trefoil.
+  The first sends $x_1$ to $r$ and $x_2$ to $s$ and the
+  other swaps which generator is sent to which generator.
+\end{example}
+
+As was implied by the prior examples, there is a relation between
+Fox $3$-coloring and the $3$-colorability of knots. In fact, it turns
+out that they are the same.
+
+\begin{theorem}
+  A knot $K$ has a $3$-coloring if and only if there is a
+  Fox $3$-coloring of $K$.
+\end{theorem}
+
+A proof of this theorem can be found in~\cite{medwid}. 
+The proof there relates two notions of coloring using
+the Wirtinger presentation to marry the conditions necessary
+for the existence of a $3$-coloring and the existence of a Fox
+$3$-coloring.
+
+\section{$n$-coloring}
+\label{sec:n-coloring}
+
+What are the benefits of looking at $3$-coloring through
+the lens of Fox $3$-coloring? Unlike with coloring diagrams,
+it is immediate that Fox $3$-coloring is a knot invariant
+as the fundamental group is invariant under homotopy equivalence, and
+so ambient isotopy as well. Another benefit
+is that it is more readily apparent how we can further
+extend Fox $3$-coloring than extending $3$-coloring. From
+the definition of $3$-coloring, there is some ambiguity that
+would need to be sorted out about precisely what rules need
+to change. For example, one of our conditions was that either
+all colors appear at a crossing or none. Since a crossing has
+at most three arcs entering it would not be possible to have
+all colors meet if we were attempting to color with more than three.
+
+This is avoided with Fox $3$-coloring. The only choice we made
+was that we are looking at homomorphisms to $D_6$. We could
+very easily have chosen any finite group and gotten the
+same nice structure that we had above. The reason that
+$D_6$ is the group used for Fox $3$-coloring is that it is
+the group of symmetries of the triangle. We can
+define the Fox $n$-coloring similarly. Let $D_{2n}$ be
+the symmetry group of a regular $n$-gon.
+
+\begin{definition}
+  Let $G$ be the knot group of a knot $K$. Then
+  a \textit{Fox $n$-coloring} of $K$ is a homomorphism $\rho: G\rightarrow D_{2n}$
+  where $\rho$ is called a \textit{non-trivial $n$-coloring} if $\rho$ is
+  surjective.
+\end{definition}
+
+We can also extend the notion of coloring that we started
+with. However, it does take more effort. Instead of choosing
+the colors that we did when originally defining $3$-coloring,
+we could just as easily have used numbers instead. Then,
+instead of requiring that each crossing either have all three
+colors appear or only a single color appear, would be equivalent to each
+crossing satisfying the equation
+\[
+  2x-y-z\equiv 0 \mod 3
+\]
+where the arcs of the crossing are labeled as in Figure~\ref{fig:numcolor}.
+
+\begin{figure}
+  \includegraphics[scale=\ds]{numcolor}
+  \caption{Colored Crossing}
+  \label{fig:numcolor}
+\end{figure}
+
+In this form, it is more apparent how we could extend $3$-coloring
+to arbitrary $n$ by simply replacing the modulus. Going back
+to our initial example of a knot, the figure-eight knot, we have
+an example of a knot that is not $3$-colorable but is 5-colorable
+as shown in Figure~\ref{fig:figure-eight-c}.
+
+\begin{figure}
+  \includegraphics[scale=\ds]{figure-eight-c}
+  \caption{Figure-eight 5-coloring}
+  \label{fig:figure-eight-c}
+\end{figure}
+
+\section*{Acknowledgments}
 \begin{thebibliography}{99}
 
-\bibitem{jpsk} Kung, J.P.S., Critical problems, in {\em Matroid  
-Theory} (eds. J. E. Bonin, J.G. Oxley, and B. Servatius), {\em  
-Contemporary Mathematics} {\bf 197}, Amer. Math. Soc., Providence,  
-1996, pp. 1--127.
+\bibitem{hatcher}  Hatcher, A., \textit{Algebraic Topology,}
+  Cambridge University Press, Cambridge, 2001.
 
+\bibitem{Livingston}  Livingston, C., \textit{Knot Theory,}
+  Mathematical Association of America, Washington DC, 1996.
+
+\bibitem{medwid}  Medwid, M., \textit{Generalized $P$-Colorings of Knots,}
+  Bowling Green University, 2014.
+
+\bibitem{Poonen}  Poonen, Bjorn. Undecidable Problems: a Sampler, in
+  \textit{Interpreting GöDel}, pp. 211241., doi:10.1017/cbo9780511756306.015.
+
+\bibitem{quickfox}  Fort, M. K., and Fox R.H.,
+  \textit{A Quick Trip Through Knot Theory}, in Topology of 3-Manifolds and
+  Related Topics, Dover Publications, Mineola, 2010.
 \end{thebibliography}

### 2018-04-26 paper/paper.tex
Finished revising paper

@@
 \maketitle
-\textbf{TODO}:
-\begin{enumerate}
-\item Remove \textbf{TODO}
-\item Iron out Figure/image placement before final edition. Too early
-  now. Wait till revision is done.
-\item Passive voice/adverbs (Hemingway App)
-\end{enumerate}
 
@@
 sort of problem. Given a circle $S^1$ what different ways can we embed
-it into $\bb{R}^3$ or $\bb{R}^3$  with an additional point at infinity ($S^3$)?
+it into $\bb{R}^3$ or $S^3$ ($\bb{R}^3$ with a point at $\infty$)?
 A typical drawing of a knot can be seen in Figure~\ref{fig:figure-eight}.
-
-\begin{figure}
-  \includegraphics[scale=\ds]{figure-eight}
-  \caption{Figure-eight knot}
-  \label{fig:figure-eight}
-\end{figure}
 
@@
 called tricolorability. Afterwards, we will look at an alternative definition
-of tricolorability. Then we will introduce notions of how one may consider
+of tricolorability that utilizes the fundamental group.
+Then we will introduce notions of how one may consider
 coloring knots with more than three colors.
+
+\begin{figure}
+  \includegraphics[scale=\ds]{figure-eight}
+  \caption{Figure-eight knot}
+  \label{fig:figure-eight}
+\end{figure}
 
@@
 The first is our notion of equivalence. Unfortunately, a homeomorphism from
-one knot to another is too weak a notion of equivalence. Instead we will
-use the following:
+one knot to another is too weak a notion of equivalence as all simple closed curves
+are homeomorphic to $S^1$. Instead we will use the following:
 
 \begin{definition}
-  Two knots $K,J$ are \textit{ambient isotopic} if there is a homotopy on the ambient
+  Two knots $K$ and $J$ are \textit{ambient isotopic} if there is a homotopy on the ambient
   space $H:S^3\times [0,1]\rightarrow S^3$ if $H(x,0)$ is the identity and the
@@
     These are called \textit{crossings}.
-  \item For any two crossings there are open disjoint neighborhoods of each.
+  \item Given any two crossings they each have an open neighborhood
+    that is disjoint from the other's neighborhood.
   \item All crossings must be either overcrossings or undercrossings.
@@
 is why we must denote all crossings as either overcrossings or undercrossings.
-This allows one to recover the knot in its entirity from the diagram. Otherwise
-it would be ambiguous what knot is recovered. The segments that make up the diagram
+This allows one to recover the knot in its entirety from the diagram. Otherwise
+it would be ambiguous what knot is recovered since we would have to make a choice
+of over or under for each crossing. The segments that make up the diagram
 are called \textit{arcs}.
@@
 for a given knot. Moreover actually telling whether two diagrams denote
-the same knot is extremely difficult although it is decidable and moreover
+the same knot is extremely difficult, though decidable, and moreover
 belongs to NP~\cite{Poonen}.
@@
 
-There are two knots that we will return to over and over again in this paper
+There are two knots that we will return to repeatedly
 as they are the simplest examples of knots for which tricolorability
@@
   For type-I we have there only a single case as a type-I move acts only on
-  a single arc.
+  a single arc as seen in Figure~\ref{fig:t1-c}.
   \begin{figure}
@@
   For type-II, there are two cases either both strands have the same color
-  or they are different.
+  or they are different as seen in Figure~\ref{fig:t2-c}.
   \begin{figure}
@@
   the colors of the strands entering. We will demonstrate
-  three such cases and the rest are similar.
+  three such cases, given in Figure~\ref{fig:t3-c}, and the rest are similar.
   \begin{figure}
@@
 it is immediate that Fox $3$-coloring is a knot invariant
-as the fundamental group is invariant under homotopy equivalence, and
-so ambient isotopy as well. Another benefit
+as the fundamental group is invariant under homotopy equivalence.
+So Fox $3$-coloring must be invariant under ambient isotopy as well. Another benefit
 is that it is more readily apparent how we can further
@@
 
-\section*{Acknowledgments}
+\pagebreak
+
 \begin{thebibliography}{99}
